\section{Application Letter}\label{sec:application-letter}
\newline
\\
To whom may concern:
\\
\paragraph{}
I am the computer science student who are looking for a summer internship before graduate
for my education.
\\
\paragraph{}
I heard 3sharp from one of my friend who was had internship with your college.
He introduces 3sharp to me and suggest me should try to apply an internship position.
Because this is a great company with a branch of nice people.
And i will learn a lot of form here.
\\
\paragraph{}
As I study form 3sharp.com.
This company is working on offer service to help customer to show their product and idea.
I also have few years marketing experience.
So for 3sharp I think I can very easy to understand the teams working on.
\\
\paragraph{}
But so far, as internship searcher for my education.
I wish I can get a internship position form you working on web develop and computer science relevance.
\\
\paragraph{}
I have ability to individually to make backend service with database and web application at the front end.
I also have some expires to working on the R language to deal with some big data.
\\
\paragraph{}
I am active person more like to make sure everything inclined to structure and systematically.
Since two years computer science study and practice.
I obtained the most important skill which is how to fast and correct to solve the problem.
\\
\paragraph{}
If I have honour to working with your intelligent college.
I will try to do my best and offer my full capacity to finish the task.
And hopefully to make my final project with company to create some interest things.
\\

\paragraph{}
\noindent \\
Yours sincerely\\
Fei Gu\\
\today